---
layout: page
title: ""
date: 2018-01-12
author: "Thomas M. Massie"
output:
  html_document:
    keep_md: true
---
<!-- mathjax: default -->




```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include = FALSE}
rm(list=ls())
```


```{r include = FALSE}
# Load libraries.
library(repmis)
library(tidyverse)
library(lubridate)
library(chron)      # https://cran.r-project.org/web/packages/sp/sp.pdf
library(sp)
library(HURDAT)
```


# Storm data preparation

Since I wnat to focus on the analysis of the storm data, I use R's [hurdat package](https://cran.r-project.org/web/packages/HURDAT/index.html), which does a lot of the cleaning for those who want to save time ([vignette](https://cran.r-project.org/web/packages/HURDAT/HURDAT.pdf)). 


## Reading the data

I read in two data sets: one for hurricanes (Atlantic ocean) and one for typhoons (northeast and central Pacific ocean). The original data format is the revised Atlantic hurricane database (HURDAT2, see [here](http://www.aoml.noaa.gov/hrd/hurdat/Data_Storm.html) for details). You probably want to have a look at the decription that is provided [here](http://www.aoml.noaa.gov/hrd/hurdat/newhurdat-format.pdf). 
To each data set I add a variable that indicates the respective ocean it belongs to.
```{r echo = TRUE, message = FALSE}
# Data for Atlantic storms.
dd.atlantic <- get_hurdat(basin = "AL") %>%
  mutate(Ocean = "Atlantic")
# Data for northeast and north-central Pacific storms.
dd.pacific <- get_hurdat(basin = "EP") %>%
  mutate(Ocean = "Pacific")
```

I combine both data sets to a single one.
```{r}
dd.org <- bind_rows(dd.atlantic, dd.pacific)
str(dd.org)
```

Next, I make a couple of adjustments so that the data set matches my needs for analysis:

- *Year*: to summarise/describe data by year.
- *DateTimeSameYear*: when you only want to explore seasonal occurances.
- *Duration*: giving amount of time s storm lasted.
- *WindKPH*: wind speed in km per hour.
- *KeyPlus*: a combination of *Key* and *Name*.
- *SaffirSimpson*: assigning storms a value on the [Saffir-Simpson scale](https://en.wikipedia.org/wiki/Saffir%E2%80%93Simpson_scale).
```{r}
dd <- dd.org %>%
  mutate(Year = year(DateTime),
         DateTimeSameYear = as.POSIXct(strptime(format(DateTime, "%m/%d %H:%M:%S"), "%m/%d %H:%M:%S")),
         WindKPH = round(Wind * 1.609344, 0),
         Duration = NA, # Needed at a latter point.
         KeyPlus = paste(Name, " (",Key,")", sep = ""),
         SaffirSimpson = ifelse(WindKPH %in% 0:62, "Tropical depression",
                                ifelse(WindKPH %in% 63:118, "Tropical storm",
                                       ifelse(WindKPH %in% 119:153, "1",
                                              ifelse(WindKPH %in% 154:177, "2",
                                                     ifelse(WindKPH %in% 178:208, "3",
                                                            ifelse(WindKPH %in% 209:251, "4", "5")))))))
```

There is one manipulation that is critical for plotting (at least) with [Leaflet for R](https://rstudio.github.io/leaflet/): All longitude values have to be positive. Otherwise Leaflet gets confused and the data "jumps" by 360\degree.
```{r}
dd$Lon <- ifelse(dd$Lon < 0, dd$Lon + 360, dd$Lon)
```

Then, for some variables it makes more sense if they are declared as factors.
```{r}
dd[c("Key", 
     "Year",
     "KeyPlus",
     "Status",
     "Ocean",
     "SaffirSimpson")] = lapply(dd[c("Key", 
                                     "Year",
                                     "KeyPlus",
                                     "Status",
                                     "Ocean",
                                     "SaffirSimpson")], as.factor)
```

Finally, I calculate the duration of each storm.
```{r}
# ids <- as.character(unique(dd$ID))
for (i in as.character(unique(dd$Key))) {
  dd.i <- filter(dd, Key == i)
  for (n in 1:length(dd.i$Key)) {
    # '%--%' is the interval operator returning the time difference (lubridate).
    dd.i$Duration[n] <- round(as.numeric(as.duration(dd.i$DateTime[1] %--% dd.i$DateTime[n]))/60/60/24, 2)
  }
  dd$Duration[which(dd$Key %in% i)] <- dd.i$Duration
}
```

There you go! 
```{r echo = FALSE}
str(dd)
```


## Storing the data set

I save the workspace for later use and exploration!
```{r}
save.image("StormDataWorkSpace.RData")
```




